---
title: Model-based estimation of outcomes and cost-effectiveness of increased naloxone distribution across channels in the United States
author: 


output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
    reference_docx: word-style-reference-manuscript.docx
bibliography: 'Opioid CEA and social outcomes-Naloxone.bib'
csl: american-medical-association-brackets.csl

header-includes:
- \usepackage{placeins}
- \usepackage{amsfonts} 
- \usepackage{amsmath}

---


\newcommand{\1}{\textbf{1}}


<br>

W. Alton Russell^1,2^, Reanna Shah^3^, Mohammad Jalali^1,2^, others tbd


<br>

^1^Institute for Technology Assessment, Massachusetts General Hospital, Boston, USA

^2^Harvard Medical School, Boston, USA

^3^Duke University, Durham, USA



<br>


**Corresponding author:** 

**Key words:** 

**Running title:** Naloxone distribution



#####

```{r setup, include=FALSE}
library(ggplot2)
library(data.table)
library(scales)
library(flextable)
library(officedown)
library(officer)
theme_set(theme_bw())
library(readxl)


```


```{r, include=FALSE}




```




# Abstract

**Background:** A

**Methods:** A

**Results:** A

**Conclusions:** A


#####


# Introduction
> A

<br>

# Methods

> A

## Sub

> A



# Results

> A

<br>

# Discussion

> A

#####

# Declarations

**Funding:** A

**Conflicts:** A

**Ethics/Consent:** A

**Data and materials:** A

**Code availability:** A

**Authors’ contributions:** 


#####

# References

<div id="refs"></div>

#####

::: {custom-style="Compact"}
| **Table 1** A
:::




<!---BLOCK_LANDSCAPE_START--->

::: {custom-style="Compact"}
| **Table 2** Estimated adverse event cases and financial burden by adverse event with and without whole blood pathogen inactivation
:::




<!---BLOCK_LANDSCAPE_STOP--->



#####
![**Fig. 1.** ]()



#####
\setcounter{page}{0}

# Supplemental materials

<br>

# A. Calculations for estimating the outcomes of pathogen inactivation


#####

::: {custom-style="Compact"}
| **Table S1** Parameters for the microcosting calculations
:::




::: {custom-style="hidden_line"}
| .
:::


#####


![]()

